### 2019-03-10 manuscript/discussion.tex
- minor fixes to the previous version of first Discussion paragraph

We investigated the individual and joint effects of ploidy and breeding system states in diversification of Solanaceae.
Most significantly, we found that the effects of ploidy, inferred as significant when it is the only trait under consideration, are trumped by breeding systems when the two traits are considered jointly.
Interestingly, the difference in diversification rates between the diploids and polyploids is negligible on the background of self-compatibility.
%B: should we mention here that the hidden states presage these results in each case? Maybe we don't want to make too much of that, but it is fairly interesting. Also possibly hit that in your paragraph(s), below.
In the same vein, the difference in diversification rates between self-incompatible and self-compatible lineages is smaller in the diploid genomic background.
In our final analyses, motivated by the widespread findings of paleopolyploid ancestry across angiosperms, we did not recover strong support for inclusion of diploidization process.
Below, we discuss the key findings, and outline a broad strategy for applying phylogenetic comparative methods in the study of complex interactions among traits, in the context of diversification.
%  Surprising outcomes: (1)  D and P on background of C, and (2) SC not as dead of an end as it was in goldberg2010, if P is partitioned out (can be framed as kind of path-dependence, i.e. qIC path different than rho path, or same as (1), so that I and C are less different on the background of D.

>>>>

%B:  at least two surprising outcomes: (1)  D and P on background of C, and (2) SC not as dead of an end as it was in goldberg2010, if P is partitioned out (can be framed as kind of path-dependence, i.e. qIC path different than rho path, or same as (1), so that I and C are less different on the background of D.
We investigated the individual and joint effects of ploidy and breeding system states in diversification of Solanaceae.
Most significantly, we found that the effects of ploidy, inferred as significant when it is the only trait under consideration, are trumped by breeding systems when the two traits are considered jointly.
Interestingly, the difference in diversification rates between the diploids and polyploids is negligible on the background of self-compatibility.
%B: should we mention here that the hidden states presage these results in each case? Maybe we don't want to make too much of that, but it is fairly interesting. Also possibly hit that in your paragraph(s), below.
In the same vein, we recovered a smaller difference in diversification rates between self-incompatible and self-compatible lineages against diploid genomic background. %B: "in diploids" may work better?
%B: need help with pathway single-sentence summary
Motivated by the widespread findings of paleopolyploid ancestry across angiosperms, we also examined support for diploidization in the history of the family, which appears to be weak. %B: "mixed" "not strong" what's the right word here?
Disentangling the patterns of diversification linked to multiple traits is difficult, but our strategy allows tests complex hypotheses regarding a heterogenous diversification process.
Below, we discuss these key findings, and outline a broad approach for application of phylogenetic comparative methods in the context of interactions among traits and diversification process.
